Elephant Seal Age JAE Intraspecific Variation

### 2023-12-05 paper/paperv3.qmd
model wont converge?

```{r}
#| label: age_breeding_mod
#| #| fig-width: 9

breeding_mod_bad <- glmer(observed_int ~ poly(age, 2) + (1 | animalID) + (1 | year),
                      data = filter(sealdat), 
                      family = "binomial")

count(sealdat, year) %>% 
     left_join(as_tibble(ranef(breeding_mod_bad)$year, 
                         rownames = "year") %>% 
                   mutate(year = as.numeric(year)) %>% 
                   rename(coef = `(Intercept)`),
               by = "year") %>%
     ggplot(aes(n, coef, color = year, label = year)) +
     geom_point() + 
  geom_label() + 
     scale_color_gradient(low = "blue", high = "red") + 
     theme_few()

breeding_mod <- glmer(observed_int ~ poly(age, 2) + (1 | animalID) + (1 | year),
                      data = filter(sealdat), 
                      family = "binomial")
breed_pred <- ggpredict(breeding_mod, terms = c("age [all]"))
summary(breeding_mod)
#table s1, look at roxannes ecology letters paper supplemental 
#Pull out the fixed effects table with 2 sfs, can paste in excel to adjust digits 
#intercept, age (linear), age (quadratic) as row names 
#in figure caption say "results from x analyis. The random effect variance of animal id is X (from results) and year was X. Apply to all the other stats. 
#analyses fit to the age in which we have larger sample sizes fit also have a quadratic fit and don't change the story

>>>>

```{r}
#| label: age_breeding_mod
#| fig-width: 9

breeding_mod <- glmer(observed_int ~ poly(age, 2) + (1 | animalID) + (1 | year),
                      data = filter(sealdat), 
                      family = "binomial")

breed_pred <- ggpredict(breeding_mod, terms = c("age [all]"))

summary(breeding_mod)

#table s1, look at roxannes ecology letters paper supplemental 
#Pull out the fixed effects table with 2 sfs, can paste in excel to adjust digits 
#intercept, age (linear), age (quadratic) as row names 
#in figure caption say "results from x analyis. The random effect variance of animal id is X (from results) and year was X. Apply to all the other stats. 
#analyses fit to the age in which we have larger sample sizes fit also have a quadratic fit and don't change the story
